Assessing primitives performance\\ on multi-stage execution \todo{modify maybe}

### 2018-06-28 paper.tex
comply with reference style
fix margin overrun

\paragraph{\GCCLinux.}The \GCCLinux evaluation was performed on an Asus Zenbook with Ubuntu 16.04 LTS, a 2.2 Ghz processor Intel Core 5, 8 Gb 1600MHz DDR3 of RAM. The Linux VM was compiled using GCC version 5.4.0.

@@

\paragraph{Processor.}The following evaluation was performed on 32 bits Intel VMs (x86).

@@

In some programming languages (Strongtalk, Self, RSqueak), the implementors tried to decrease the overall number of optional primitives by improving the client language performance, reducing the need for such primitives \cite{Strongtalk, ursPHD, NoPrimTracing}. In other work \cite{Ball86a, Char13a}, optional primitives can be written directly in a subset of the client language and compiled at runtime to native code, hence they can be modified in the client language without recompiling the VM. Lastly, several VMs implemented their interpreter on top of an abstract assembly~\cite{V8,LLIntJSC}, allowing the interpreter to use the same register conventions as the code generated by the JIT and avoiding the stack switch cost.

@@

% The 'abbrvnat' bibliography style is recommended.
\bibliographystyle{alpha}
\bibliography{sista,rmod,others}
%\bibliographystyle{abbrvnat}
%
%% The bibliography should be embedded for final submission.
%
%\begin{thebibliography}{}
%\softraggedright
%
%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...
%
%\end{thebibliography}

>>>>

\paragraph{\GCCLinux.}The \GCCLinux evaluation was performed on an Asus Zenbook with Ubuntu 16.04.4 LTS, a 2.2 Ghz processor Intel Core 5, 8 Gb 1600MHz DDR3 of RAM. The Linux VM was compiled using GCC version 5.4.0.

@@

\paragraph{}The following evaluation was performed on 32 bits Intel VMs (x86).

@@

In some programming languages (Strongtalk, Self, RSque-ak), the implementors tried to decrease the overall number of optional primitives by improving the client language performance, reducing the need for such primitives \cite{Strongtalk, ursPHD, NoPrimTracing}. In other work \cite{Ball86a, Char13a}, optional primitives can be written directly in a subset of the client language and compiled at runtime to native code, hence they can be modified in the client language without recompiling the VM. Lastly, several VMs implemented their interpreter on top of an abstract assembly~\cite{V8,LLIntJSC}, allowing the interpreter to use the same register conventions as the code generated by the JIT and avoiding the stack switch cost.

@@

% The 'abbrvnat' bibliography style is recommended.
%\bibliographystyle{alpha}
\bibliographystyle{abbrvnat}
\bibliography{sista,rmod,others}

%
%% The bibliography should be embedded for final submission.
%
%\begin{thebibliography}{}
%\softraggedright
%
%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
%P. Q. Smith, and X. Y. Jones. ...reference text...
%
%\end{thebibliography}
